Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-03-15 analysis/paper/paper.Rmd
Clean up data collection and analysis section

Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. Five and four disease assessments were made in 2015 and 2016, respectively. Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models. We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season. Our findings indicate that farmers can safely adopt the AWD technology without risk of increasing sheath blight disease.

>>>>

Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. Five and four disease assessments were made in 2015 and 2016, respectively.
